Estimating the replicability of psychology experiments after an initial failure to replicate

### 2024-04-01 manuscript/manuscript.Rmd

@@

All of the correlations are presented in Figure \@ref(tab:cor-table).
The number of rescues is small, and many of these predictors are correlated, so we caution against over interpretation. 
The strongest correlates of rescue success were open materials, a small sample size on the first replication, a small sample size on the first replication relative to the original sample size, and a large rescue sample size relative to the first replication.
None of the pre-registered correlates meet the conventional significance threshold; the two correlates based on ratios that reflect a relatively smaller replication sample size are marginally significant.

@@

<!-- (TODO other successes or failures we want to discuss? ) (Ben: Emily's project was interesting: the rescue succeeded but with big stimulus-level random effects. Verity's project was also interesting: the previous replication, as well as another in the literature, showed similar but smaller findings and it really looked like she could get the effect with a bigger sample, but she ended up finding totally different results.) -->

>>>>

TODO FIX CITATION / BIB INFO (re OSC for RP:P but only after we unlink from zotero)

@@

All of the correlations are presented in Figure \@ref(tab:cor-table).
The number of rescues is small, and many of these predictors are correlated, so we caution against over interpretation.

The strongest correlates of rescue success were open materials, a small sample size on the first replication, a small sample size on the first replication relative to the original sample size, and a large rescue sample size relative to the first replication.
None of the pre-registered correlates meet the conventional significance threshold; the two correlates based on ratios that reflect a relatively smaller replication sample size are marginally significant.

@@

\@child2018 studied reading times for passages of text with different emotional valences written from either a third-person or second-person perspective.
They found a significant interaction between perspective and valence: participants read positively-valenced passages faster than negatively-valenced passages, but only when they were written from a second-person perspective.
The first replication used a similar sample size to the original study (40) and found an effect that trended in the same direction, but was substantially smaller.
The rescuer identified several possible reasons for this failure, foremost among them that the replication was conducted online while the original was conducted in person.
It is reasonable to expect online studies of reading time to be noisier than in-person studies because the environments participants completed the study in varied much more online.
The rescue attempt was still online, but used a much larger sample size to account for noisier data.
Still, the rescue found a non-significant effect that trended in the opposite direction from the original and first replication.
Even though the first replication trended in the same direction and there was an identifiable reason for the smaller effect size, increasing sample size did not rescue the effect.
